### 2024-02-05 Paper/main.tex
added file to work on the paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{NAO robot that imitates human movements using Mediapipe\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Costilla Caballero, Salvador}
\IEEEauthorblockA{\textit{Applied Robotics } \\
\textit{Hof University of Applied Science}\\
CDMX, Mexico \\
salvadorcoscab@gmail.com}
}

\maketitle

\begin{abstract}

This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction and state of the art}
In this project we tryied to make a NAO robot from Aldebaran move imitating human movements. This movements were captured with a webcam using Mediapipe.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-02-13 Paper/main.tex
added file to work on the paper

@@
 \title{NAO robot that imitates human movements using Mediapipe\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+
 }
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Costilla Caballero, Salvador}
+\author{\IEEEauthorblockN{Costilla Caballero, Salvador}
 \IEEEauthorblockA{\textit{Applied Robotics } \\
@@
 
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+    In this project I made a NAO robot, from Aldebaran, move imitating human movements. This movements were captured with a webcam using Mediapipe.
+    Though this human imitation has already been done, I wanted to make it in a different way. Because most of the other projects use multiple cameras or depth sensors, such as the LIDAR sensor. 
+    The project is way far from being finished, because the robot only moves his hands and not very precisely. But I think is a good start for future work on computer vision and robotics.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+NAO, Mediapipe, Human imitation, aldebaran, robotics
 \end{IEEEkeywords}
+% State of the art
+\section{State of the art}
+In this section I will describe different ways to move a NAO robot the Mediapipe Framework and a work related to human imitation using the NAO robot.
 
-\section{Introduction and state of the art}
-In this project we tryied to make a NAO robot from Aldebaran move imitating human movements. This movements were captured with a webcam using Mediapipe.
+The NAO robot docomentation  \cite{b7} states that there is two ways to move the NAO robot to do poses.
+The first one is using the angles from the joints and the second one is using inverse kinematics.
+Though there is more ways to move the robot, those are more for walking or to perform a specific pose.
 
-\section{Ease of Use}
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
+There is  two way to control the effectors to perform a pose, regardless we use inverse kinematics or not, which are:
 \begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+    \item Animation methods, in which the time is fixed and there are blocking functions.
+    \item Reactive methods, that can be used to control the robot in real time, and there are non-blocking functions.
 \end{itemize}
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
+We have various functions contained in the \textit{ALMotionProxy} module, related to the movement by controlling the joints some of the animation methods are:
+\begin{itemize}
+    \item \textit{ALMotionProxy.angleInterpolation}, that allows you to move the robot from a specific position to another in a specific time.
+    \item \textit{ALMotionProxy.angleInterpolationWithSpeed}, that allows you to move the robot from a specific position to another in a specific time and speed.
+\end{itemize}
+One important method is:
+\begin{itemize}
+    \item \textit{ALMotionProxy.setAngles}, that allows you to move set the angles of a single joint or a set of joints of the robot.
+\end{itemize}
+
+As it was stated before the robot can be controlled using inverse kinematics as well, in this case a classical IK solver which uses only the joints of the effector chain to reach a target and a generalized IK solver (also called Whole Body control) which uses all the robot joints to reach a target.
+Some of the animation and reactive methods related to the inverse kinematics that I consider important are:
+\begin{itemize}
+    \item \textit{ALMotionProxy.positionInterpolation} that allows you to move the robot from a specific position to another in a specific time 
+    \item \textit{ALMotionProxy.setPosition}, that allows you to move the robot to a specific position in a 3d space.
+\end{itemize}
+
+BlazePose \cite{b7}, is and architecture for single person 3D pose detection based in convolutional neural networks.
+It is available in the Mediapipe framwork.
+And allows you to detect poses from a video or an image.
+There are 33 landmarks that the BlazePose model can detect (See figure \ref{fig:landmarksMP}). 
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=0.4\textwidth]{images/landmarksMP.jpeg}}
+    \caption{Landmarks from the Mediapipe library.}
+    \label{fig:landmarksMP}
+\end{figure}
+These landmarks can be read as a set of points in a 3D space.
+The Landmarker has various configuration options, such as:
+\begin{itemize}
+\item \textit{model\_complexity},  that allows you to choose between three different models, the lite, the full and the heavy. Depending on the model chosen the accuracy and the speed can increase.
+\item \textit{min\_detection\_confidence}, that allows you to set the minimum confidence that a pose is detected.
+\item \textit{min\_tracking\_confidence}, that allows you to set the minimum confidence that a pose is tracked.
+\end{itemize}
+
+In \cite{b7} the authors use the NAO robot to imitate the movements of a human using a kinect sensor. 
+They use a client-server approach to send the data from the kinect sensor to the robot.
+In the client part they use the \textit{pykinect2} library to get the data from the kinect sensor, this data are 25 landmarks that represent the human body.
+These data is then sent to the server part using the \textit{socket} library.
+In the server part they calculate the angles between the joints and then send them to the robot using the \textit{ALMotionProxy.AngleInterpolation} method.
+
+% intrduccion: poner en contexto al lector sobre el tema
+% Se describe el orden de los estudios
+% revisar el proyecto del kinect 
+% revisar formas de conectar multiples versiones de python
+% revisar mediapipe pose estimation
+% revisar NAOqi API
+% revisar robot NAO
+% investigaciones, proyectos, papers, etc.: describir nombres de las referenciadas
+% conclusiones de la investigacion
+
+\section{Approach}
+
+\subsection{Objectives}
+
+During this project I had some objectives which were:
+\begin{itemize}
+\item Solve the computer vision part, that in this case was done with Mediapipe.
+\item Make the robot move using the NAOqi API.
+
+\end{itemize}
+The problems were that, in order to work with the NAOqi API, I had to download and setup the SDK which is written (by the moment of this project) in Python 2.7 and the Mediapipe is only availble in Python 3.7 or higher.
+That is why I had to add as an objective to make the two libraries work together.
+
+% Methodology
+\subsection{Methodology}
+The methodology that I used to solve the objectives above was to first divide the problem into modules and tried to solve them separately, and then join them together and solve the problems that arose from the connection between the two modules.
+The main two modules were the computer vision and the robot movement.
+
+\subsection{Computer vision}
+% Begin with the computer vision part and the NAOqi API part
+In the beginning, the computer vision part was done very easily, because Mediapipe has a lot of usage examples and good documentation.
+On the other hand working with the NAO robot was a much more difficult.
+\\
+For the computer vision part I used the opencv library to get images from both camera and videos and then I used the Mediapipe library to get the poses from the images.
+I used also the opencv library to plot the landmarks that the Mediapipe library detected, so I could see how the landmarks were being detected.
+This landmarks conform an object with 33 points, which represents landmarks of the human body.
+(See figure \ref{fig:landmarksMP})
+
+\subsection{Robot movement}
+
+Then I started working with the robot movement part, to do this I used the NAOqi API.
+I realized, after reading the NAOqi documentation that there is two ways to control the robot for doing poses.
+The first one was using angles and the second one was using inverse kinematics.
+I decided to use the first one because I thought that with the landmarks, obtained with Mediapipe, I could easily get the angles of each join of the robot, and also the project that I found on internet used this approach.
+All of this joint-angle approach is written in the \textit{ALMotion} module of the NAOqi API. 
+In summary the robot has various joints, and each joint can be moved using a specific angle.
+These joints work in a similar way as the human body joints, allowing some joints to pitch, roll, and yaw.
+(See figure \ref{fig:RightArmAngles})
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=0.4\textwidth]{images/RightArmAngles.jpeg}}
+    \caption{Landmarks from the Mediapipe library.}
+    \label{fig:RightArmAngles}
+    \end{figure}
+
+% connection between the two parts
+\subsection{Connection between the Computer vision and the Robot movement}
+After doing some testing on both parts, I had to somehow connect them.
+In order to do the connection between the robot and the computer vision part, I tried with \textit{execnet}, which is a library that allows you to trigger python scripts from another python script, even with different versions of python.
+But I had some problems sending the data from the computer vision part to the part in which I move the robot, so I decided to try a different approach.
+
+I decided to use sockets to send the data, as I got inspiration from a project that I found with a similiar approach, in which the author used sockets to send the data from a kinect sensor to the robot.
+This solved everything, about the connection between the scripts, because it uses the client-server approach, allowing me to use python 3.10 for the computer vision part that is the client and python 2.7 for the Robot movement part that is the server.
+I just had to do some encoding to send the data.
+
+% testing the implemented code
+\subsection{Testing the implemented code and solving problems}
+After changing the code that I found to work with Mediapipe and OpenCV instead of the kinect sensor.
+I did some testing on the functions that were already implemented in the server side, but they performed very bad, but at least, I saw that the robot moved.
+
+Also the display of the images was very slow since the code had a delay to send the data, in order for the server to process it.
+I solved this using a thread to get the data from the displayed image and send it to the server with the thread without messing up with the display.
+\\
+As I said before after changing a lot the parameters and definition of the functions that were implemented before I realized that I was not sending the right data to the robot from the server, so I decided to change the approach and instead of sending the coordenates of the landmarks to the server, I decided to send the angles between them and send them directly to the server.
+This would help me to see what angles I was sending to the robot by showing them on the displayed image.
+
+After I was able to see the angles that were being sent to the robot, I realized that the angles sent were not very good in the function definition, this is because the kinect sensor and Mediapipe have different coordenate systems, so I had to change the defintion of the functions.
+\\
+This did not work very well, though the movements were more accurate, the robot was not imitating the movement of the hands perfectly.
+So I decided to change the function.
+Instead of using geometry I tried with vectors and the angles between them.
+
+\subsection{Vector approach}
+I saw that as I had the landmarks, that represents a point in the space, I could calculate a vector between two points (See equation \ref{eq:vector}), and I could use the angles between the vectors to move the robot (See equation \ref{eq:angle}).
+But then I realized that I could also calculate the angles between the projection of the vectors (See equation \ref{eq:proy}) in a generated plane from a normal vector (See equations \ref{eq:plano},\ref{eq:p},\ref{eq:p0}).
+I tried this for one joint, that was the right shoulder pitch.
+I got the normal vector from the left shoulder to the right shoulder to generate the plane, and then I got the vectors from the right shoulder to the right elbow and from the shoulder to the right hip.
+I projected these vectors in the generated plane and then I calculated the angles between them.
+% ecuacion para obtener un vector entre dos puntos
+\begin{equation}\label{eq:vector}
+    \vec{v} = \vec{p_2} - \vec{p_1}
 \end{equation}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+% ecuacion para el angulo entre dos vectores para los angulos en el plano generado por el vector normal
+\begin{equation}\label{eq:angle}
+    \cos(\theta) = \frac{\vec{v} \cdot \vec{w}}{\| \vec{v} \| \| \vec{w} \|}
+\end{equation}
+% ecuacion de la proyeccion de un vector en el plano esto nos da un vector en el plano generado por el vector normal
+\begin{equation}\label{eq:proy}
+    proy_H \vec{v} = \left( \vec{v} \cdot \vec{u_1} \right) \vec{u_1} + \left( \vec{v} \cdot \vec{u_2} \right) \vec{u_2}
+\end{equation}
 
-\subsection{\LaTeX-Specific Advice}
+ % Ecuación del plano con un punto y un vector normal
+ \begin{subequations}
+    \begin{align}
+        \vec{n} \cdot (\vec{p} - \vec{p_0}) &= 0 \label{eq:plano} \\
+        \vec{p} &= \begin{bmatrix}
+        x \\
+        y \\
+        z
+        \end{bmatrix} \label{eq:p} \\
+        \vec{p_0} &= \begin{bmatrix}
+        x_0 \\
+        y_0 \\
+        z_0
+        \end{bmatrix} \label{eq:p0}
+    \end{align}
+ \end{subequations}
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
+I implemented a function in python to do the calculations mentioned above and this function did not work well neither when I tested it, and as could see the angles on the displayed image, I realized that the Mediapipe library did not detect the z axis very well.
+Then I remembered that the kinect sensor has a LIDAR sensor, that allows him to detect, not only position in x and y, but also depth in a better way than the Mediapipe library.
+That is why I did not continue with this approach and as I did not have more time to finish the project, I decided to leave the functions that were already implemented.
 
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
+% CONTRIBUCIONES
+\section{Contribution}
+% diferencias entre mi proyecto y los otros y como contribuye mi proyecto al estado del arte
+The main difference between my project and the others is that it has a different approach to solve the problem, relying only on one camera and machine learning to detect and recreate the human poses, instead of using a lot of sensors.
+This is a contribution to the state of the art, because it implies that if there were better machine learning models, the robot could imitate the human movements in a better way.
 
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
+\section{Experiments}
+% how is the set up to do the experiments
 
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
+% contrains of the experiments
+% results of the experiments and description of data
 
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
+\section{Conclusion and future work}
 
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
+% Acknowledgment
 \section*{Acknowledgment}
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+The authors would like to thank the support of the Hof University of Applied Science and the support of the Applied Robotics department.
 
-\section*{References}
+% Bibliography
 
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
+% para citar \cite{b7}.
 \begin{thebibliography}{00}
@@
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2024-02-13 GetAnglesNew.py

@@ -3,7 +3,22 @@
 import cv2
 import mediapipe as mp
 import numpy as np
+import matplotlib.pyplot as plt
 import sys
+import time
+import random
+def plotsomethinginrandom3d(fig):
+    x=np.random.rand(10)
+    y=np.random.rand(10)
+    z=np.random.rand(10)
+    ax.set_xlabel('X Label')
+    ax.set_ylabel('Y Label')
+    ax.set_zlabel('Z Label')
+    ax = fig.add_subplot(111, projection='3d')
+    ax.scatter(x, y, z, c='r', marker='o')
+    plt.show()
+    print(x,y,z)    
+
 def angle_between_vectors(v1, v2, normal_vector):
     v1 = np.array(v1)
     v2 = np.array(v2)
@@ -52,7 +67,7 @@ def LandMarksCapture(video):
 
 
     ## Setup mediapipe instance
-    with mp_pose.Pose(min_detection_confidence=0.5, min_tracking_confidence=0.5) as pose:
+    with mp_pose.Pose(min_detection_confidence=0.5, min_tracking_confidence=0.5,model_complexity=2) as pose:
         while True:
             ret, frame = cap.read()
             # Flip the frame horizontally
@@ -88,14 +103,12 @@ def LandMarksCapture(video):
                 RHip = [landmarks[mp_pose.PoseLandmark.RIGHT_HIP.value].x,landmarks[mp_pose.PoseLandmark.RIGHT_HIP.value].y,landmarks[mp_pose.PoseLandmark.RIGHT_HIP.value].z]
 
 
-                # calculate angle RShoulderPitch
-                angleRShoulderPitchDegrees = angleRShoulderPitch(Lshoulder,RHip,Rshoulder, Relbow)
-
 
                 # NOTE Calculations for the right arm
-                # calculate angle RShoulderPitch
 
-                angleRShoulderPitchDegrees = 100
+
+                # calculate angle RShoulderPitch
+                angleRShoulderPitchDegrees = angleRShoulderPitch(Lshoulder,RHip,Rshoulder,Relbow)
                 # Visualize angle with bigger letters
                 cv2.putText(image, f"Right Shoulder Pitch: {angleRShoulderPitchDegrees:.2f} deg",
                             [100,50],cv2.FONT_HERSHEY_SIMPLEX, 1.0, colorlabels, 2, cv2.LINE_AA)
@@ -177,6 +190,11 @@ if __name__ == "__main__":
     if len(sys.argv) > 1:
[…]

### 2024-02-13 MoveRobot.py

@@ -1,35 +1,104 @@
-import naoqi
-from naoqi import ALProxy
-import math
-#program to see the angles in the robot
-RobotIP = "salvadors-macbook-pro.local."
-RobotPort = 9559
-#Sends processed frames to the robot
-def sendrobot(robotIP="192.168.171.141", PORT=9559):
-    try:
-        try:
-            motionProxy = ALProxy("ALMotion", robotIP, PORT) #creates proxy to call specific functions
-        except Exception, e:
-            print "Could not create proxy to AlMotion"
-            print "Error was: ", e
-        try:
-            postureProxy = ALProxy("ALRobotPosture", robotIP, PORT) #creates proxy to call specific functions
-        except Exception, e:
-            print "Could not create proxy to ALRobotPosture"
-            print "Error was: ", e
+# import naoqi
+# from naoqi import ALProxy
+# import math
+# #program to see the angles in the robot
+# RobotIP = "salvadors-macbook-pro.local."
+# RobotPort = 9559
+# #Sends processed frames to the robot
+# def sendrobot(robotIP="192.168.171.141", PORT=9559):
+#     try:
+#         try:
+#             motionProxy = ALProxy("ALMotion", robotIP, PORT) #creates proxy to call specific functions
+#         except Exception, e:
+#             print "Could not create proxy to AlMotion"
+#             print "Error was: ", e
+#         try:
+#             postureProxy = ALProxy("ALRobotPosture", robotIP, PORT) #creates proxy to call specific functions
+#         except Exception, e:
+#             print "Could not create proxy to ALRobotPosture"
+#             print "Error was: ", e
 
-        # set RShoulderpitch to 0.5 radians (28.6478897565 degrees)
-        angle = -119
-        angle=math.radians(angle)
-        motionProxy.setAngles("RShoulderPitch", angle, 0.5)
-        postureProxy.goToPosture("StandInit", 0.5)
-        angle = -76
-        angle=math.radians(angle)
-        motionProxy.setAngles("RShoulderRoll", angle, 0.5)
-    except Exception, e:
-        print "Could not create proxy to ALMotion"
-        print "Error was: ", e
+#         # set RShoulderpitch to 0.5 radians (28.6478897565 degrees)
+#         angle = -119
+#         angle=math.radians(angle)
+#         motionProxy.setAngles("RShoulderPitch", angle, 0.5)
[…]

### 2024-02-13 client.py

@@ -275,7 +275,7 @@ def LandMarksCapture(getcamera):
     mp_pose = mp.solutions.pose  # Mediapipe Solutions
     cap = cv2.VideoCapture(getcamera)
     font_size = 0.7
-    with mp_pose.Pose(min_detection_confidence=0.5, min_tracking_confidence=0.5) as pose:
+    with mp_pose.Pose(min_detection_confidence=0.5, min_tracking_confidence=0.5, model_complexity=2) as pose:
         # NOTE: Descomentar para la conexión
         sock = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
         server_address = ('localhost', 10000)

### 2024-02-13 server.py

@@ -13,8 +13,10 @@ import numpy as np
 listAngles = []
 t = 0
 # change the IP to the IP of the robot or the IP of the computer that is running the simulator
-RobotIP = "192.168.171.141"
+# RobotIP = "192.168.171.141"
+# RobotIP = "192.168.171.148"
 # RobotIP = "salvadors-macbook-pro.local."
+RobotIP = ""
 RobotPort = 9559
 #Sends processed frames to the robot
 def sendrobot(anglelist, robotIP="192.168.171.141", PORT=9559):
@@ -55,7 +57,6 @@ def sendrobot(anglelist, robotIP="192.168.171.141", PORT=9559):
         isAbsolute = True #  joint positions absolute and not relative
         print(angleLists)
         motionProxy.angleInterpolation(names, angleLists, timeLists, isAbsolute) #the function= talks with the robot
-      
         print "done"
         t += 1 
     except Exception: # checks for any and all errors
@@ -69,7 +70,9 @@ def sendrobot(anglelist, robotIP="192.168.171.141", PORT=9559):
 
 
 
-def ConnectionServer():
+def ConnectionServer(ipaddresss):
+    global RobotIP
+    RobotIP = ipaddresss
     # Create a TCP/IP socket
     sock = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
 
@@ -116,7 +119,11 @@ def ConnectionServer():
 
 
 
-if __name__ == '__main__':
-    ConnectionServer()
+
+if __name__ == "__main__":
+    if len(sys.argv) > 1:
+        ConnectionServer(sys.argv[1])
+    else:
+        ConnectionServer("salvadors-macbook-pro.local.")
     
 

### 2024-02-14 Paper/main.tex
[update] paper

@@
 \begin{abstract}
-
-    In this project I made a NAO robot, from Aldebaran, move imitating human movements. This movements were captured with a webcam using Mediapipe.
-    Though this human imitation has already been done, I wanted to make it in a different way. Because most of the other projects use multiple cameras or depth sensors, such as the LIDAR sensor. 
-    The project is way far from being finished, because the robot only moves his hands and not very precisely. But I think is a good start for future work on computer vision and robotics.
+In this project we made a NAO robot, from Aldebaran, move imitating human movements. This movements were captured with a webcam using Mediapipe.
+Though this human imitation has already been done, we wanted to make it in a different way. Because most of the other projects use multiple cameras or depth sensors, such as the LIDAR sensor. 
+The project is way far from being finished, because the robot only moves his arms and not very precisely. But we think is a good start for future work on computer vision and robotics.
 \end{abstract}
@@
 \section{State of the art}
-In this section I will describe different ways to move a NAO robot the Mediapipe Framework and a work related to human imitation using the NAO robot.
+In this section we will describe different ways to move a NAO robot the Mediapipe Framework and a work related to human imitation using the NAO robot.
 
-The NAO robot docomentation  \cite{b7} states that there is two ways to move the NAO robot to do poses.
+The NAO robot docomentation  \cite{b1} states that there is two ways to move the NAO robot to do poses.
 The first one is using the angles from the joints and the second one is using inverse kinematics.
-Though there is more ways to move the robot, those are more for walking or to perform a specific pose.
+Though there is more ways to move the robot, those are more for walking or to perform a predefined pose.
 
-There is  two way to control the effectors to perform a pose, regardless we use inverse kinematics or not, which are:
+There is  two ways to control the effectors to perform a pose, regardless we use inverse kinematics or not, which are:
 \begin{itemize}
@@
 As it was stated before the robot can be controlled using inverse kinematics as well, in this case a classical IK solver which uses only the joints of the effector chain to reach a target and a generalized IK solver (also called Whole Body control) which uses all the robot joints to reach a target.
-Some of the animation and reactive methods related to the inverse kinematics that I consider important are:
+Some of the animation and reactive methods related to the inverse kinematics that we consider important are:
 \begin{itemize}
@@
 
-BlazePose \cite{b7}, is and architecture for single person 3D pose detection based in convolutional neural networks.
-It is available in the Mediapipe framwork.
+BlazePose \cite{b2}, is and architecture for single person 3D pose detection based in convolutional neural networks.
+It is available in the Mediapipe framework.
 And allows you to detect poses from a video or an image.
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics[width=0.4\textwidth]{images/landmarksMP.jpeg}}
+    \centerline{\includegraphics[width=0.48\textwidth]{images/landmarksMP.jpeg}}
     \caption{Landmarks from the Mediapipe library.}
@@
 
-In \cite{b7} the authors use the NAO robot to imitate the movements of a human using a kinect sensor. 
-They use a client-server approach to send the data from the kinect sensor to the robot.
+In a thesis called "
+Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad"\cite{b3} the authors use the NAO robot to imitate the movements of a human using a kinect sensor. 
+They use a client-server approach to send the data from the kinect sensor to the robot through the NAOqi API.
 In the client part they use the \textit{pykinect2} library to get the data from the kinect sensor, this data are 25 landmarks that represent the human body.
@@
 
-During this project I had some objectives which were:
+During this project we had some objectives which were:
 \begin{itemize}
@@
 \end{itemize}
-The problems were that, in order to work with the NAOqi API, I had to download and setup the SDK which is written (by the moment of this project) in Python 2.7 and the Mediapipe is only availble in Python 3.7 or higher.
-That is why I had to add as an objective to make the two libraries work together.
+The problems were that, in order to work with the NAOqi API, we had to download and setup the SDK which is written (by the moment of this project) in Python 2.7 and the Mediapipe is only availble in Python 3.7 or higher.
+That is why we had to add as an objective to make the two libraries work together.
 
@@
 \subsection{Methodology}
-The methodology that I used to solve the objectives above was to first divide the problem into modules and tried to solve them separately, and then join them together and solve the problems that arose from the connection between the two modules.
+The methodology that we used to solve the objectives above was to first divide the problem into modules and try to solve them separately, and then join them together and solve the problems that arose from the connection between the two modules.
 The main two modules were the computer vision and the robot movement.
@@
 \\
-For the computer vision part I used the opencv library to get images from both camera and videos and then I used the Mediapipe library to get the poses from the images.
-I used also the opencv library to plot the landmarks that the Mediapipe library detected, so I could see how the landmarks were being detected.
-This landmarks conform an object with 33 points, which represents landmarks of the human body.
+For the computer vision part we used the opencv library to get images from both camera and videos and then we used the Mediapipe library to get the poses from the images.
+We used also the opencv library to plot the landmarks that the Mediapipe library detected, so  we could see how the landmarks were being detected.
+This landmarks conformed an object with 33 points, which represents landmarks of the human body.
 (See figure \ref{fig:landmarksMP})
@@
 
-Then I started working with the robot movement part, to do this I used the NAOqi API.
-I realized, after reading the NAOqi documentation that there is two ways to control the robot for doing poses.
+Then we started working with the robot movement part, to do this we used the NAOqi API.
+We realized, after reading the NAOqi documentation that there is two ways to control the robot for doing poses.
 The first one was using angles and the second one was using inverse kinematics.
-I decided to use the first one because I thought that with the landmarks, obtained with Mediapipe, I could easily get the angles of each join of the robot, and also the project that I found on internet used this approach.
+We decided to use the first one because we thought that with the landmarks, obtained with Mediapipe, we could easily get the angles of each join of the robot, and also the project that we found on internet used this approach.
 All of this joint-angle approach is written in the \textit{ALMotion} module of the NAOqi API. 
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics[width=0.4\textwidth]{images/RightArmAngles.jpeg}}
+    \centerline{\includegraphics[width=0.5\textwidth]{images/RightArmAngles.jpeg}}
     \caption{Landmarks from the Mediapipe library.}
@@
 \subsection{Connection between the Computer vision and the Robot movement}
-After doing some testing on both parts, I had to somehow connect them.
-In order to do the connection between the robot and the computer vision part, I tried with \textit{execnet}, which is a library that allows you to trigger python scripts from another python script, even with different versions of python.
-But I had some problems sending the data from the computer vision part to the part in which I move the robot, so I decided to try a different approach.
+After doing some testing on both parts, we had to somehow connect them.
+In order to do the connection between the robot and the computer vision part, we tried with \textit{execnet}, which is a library that allows you to trigger python scripts from another python script, even with different versions of python.
+But we had some problems sending the data from the computer vision part to the part in which we move the robot, so we decided to try a different approach.
 
-I decided to use sockets to send the data, as I got inspiration from a project that I found with a similiar approach, in which the author used sockets to send the data from a kinect sensor to the robot.
+We decided to use sockets to send the data, as we got inspiration from a project that we found with a similiar approach, in which the author used sockets to send the data from a kinect sensor to the robot.
 This solved everything, about the connection between the scripts, because it uses the client-server approach, allowing me to use python 3.10 for the computer vision part that is the client and python 2.7 for the Robot movement part that is the server.
-I just had to do some encoding to send the data.
+We just had to do some encoding to send the data.
 
@@
 \subsection{Testing the implemented code and solving problems}
-After changing the code that I found to work with Mediapipe and OpenCV instead of the kinect sensor.
-I did some testing on the functions that were already implemented in the server side, but they performed very bad, but at least, I saw that the robot moved.
+After changing the code that we found to work with Mediapipe and OpenCV instead of the kinect sensor.
+We did some testing on the functions that were already implemented in the server side, but they performed very bad, but at least, we saw that the robot moved.
 
 Also the display of the images was very slow since the code had a delay to send the data, in order for the server to process it.
-I solved this using a thread to get the data from the displayed image and send it to the server with the thread without messing up with the display.
+We solved this using a thread to get the data from the displayed image and send it to the server with the thread without messing up with the display.
 \\
-As I said before after changing a lot the parameters and definition of the functions that were implemented before I realized that I was not sending the right data to the robot from the server, so I decided to change the approach and instead of sending the coordenates of the landmarks to the server, I decided to send the angles between them and send them directly to the server.
-This would help me to see what angles I was sending to the robot by showing them on the displayed image.
+As we said before after changing a lot the parameters and definition of the functions that were implemented before we realized that we was not sending the right data to the robot from the server, so we decided to change the approach and instead of sending the coordenates of the landmarks to the server, we decided to send the angles between them and send them directly to the server.
+This would help me to see what angles we was sending to the robot by showing them on the displayed image.
 
-After I was able to see the angles that were being sent to the robot, I realized that the angles sent were not very good in the function definition, this is because the kinect sensor and Mediapipe have different coordenate systems, so I had to change the defintion of the functions.
+After we was able to see the angles that were being sent to the robot, we realized that the angles sent were not very good in the function definition, this is because the kinect sensor and Mediapipe have different coordenate systems, so we had to change the defintion of the functions.
 \\
 This did not work very well, though the movements were more accurate, the robot was not imitating the movement of the hands perfectly.
-So I decided to change the function.
-Instead of using geometry I tried with vectors and the angles between them.
+So we decided to change the function.
+Instead of using geometry we tried with vectors and the angles between them.
 
 \subsection{Vector approach}
-I saw that as I had the landmarks, that represents a point in the space, I could calculate a vector between two points (See equation \ref{eq:vector}), and I could use the angles between the vectors to move the robot (See equation \ref{eq:angle}).
-But then I realized that I could also calculate the angles between the projection of the vectors (See equation \ref{eq:proy}) in a generated plane from a normal vector (See equations \ref{eq:plano},\ref{eq:p},\ref{eq:p0}).
-I tried this for one joint, that was the right shoulder pitch.
-I got the normal vector from the left shoulder to the right shoulder to generate the plane, and then I got the vectors from the right shoulder to the right elbow and from the shoulder to the right hip.
-I projected these vectors in the generated plane and then I calculated the angles between them.
+We saw that as we had the landmarks, that represents a point in the space, we could calculate a vector between two points (See equation \ref{eq:vector}), and we could use the angles between the vectors to move the robot (See equation \ref{eq:angle}).
+But then we realized that we could also calculate the angles between the projection of the vectors (See equation \ref{eq:proy}) in a generated plane from a normal vector (See equations \ref{eq:plano},\ref{eq:p},\ref{eq:p0}).
+We tried this for one joint, that was the right shoulder pitch.
+We got the normal vector from the left shoulder to the right shoulder to generate the plane, and then we got the vectors from the right shoulder to the right elbow and from the shoulder to the right hip.
+We projected these vectors in the generated plane and then we calculated the angles between them.
 % ecuacion para obtener un vector entre dos puntos
@@
 
-I implemented a function in python to do the calculations mentioned above and this function did not work well neither when I tested it, and as could see the angles on the displayed image, I realized that the Mediapipe library did not detect the z axis very well.
-Then I remembered that the kinect sensor has a LIDAR sensor, that allows him to detect, not only position in x and y, but also depth in a better way than the Mediapipe library.
-That is why I did not continue with this approach and as I did not have more time to finish the project, I decided to leave the functions that were already implemented.
+We implemented a function in python to do the calculations mentioned above and this function did not work well neither when we tested it, as we could see the angles on the displayed image, we realized that the Mediapipe library did not detect the z axis very well, even with a more complex model.
+Then we remembered that the kinect sensor has a LIDAR sensor, that allows him to detect, not only position in x and y, but also depth in a better way than the Mediapipe library.
+That is why we did not continue with this approach and as we did not have more time to finish the project, we decided to leave the functions that were already implemented.
 
@@
 This is a contribution to the state of the art, because it implies that if there were better machine learning models, the robot could imitate the human movements in a better way.
+There is also a contribution to the work done before in "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad" \cite{b3}, because we can see the angles that are being sent to the robot, which can be useful for further research.
 
@@
 % how is the set up to do the experiments
+To do the experiments and testing we used Choreographe, which has a simulator mode, in which you can see a NAO robot and move it using the localhost as the robot IP (See figure \ref{RobotSimulation}).
+We used this to test the robot movements, but we also used a real robot to see the movements in a real robot (See figure \ref{RobotWorking}).
+We had a script to try the robot movments and another script just to try the computer vision part.
+The union of both scripts, as we said before, was done using sockets.
+So we had to run two scripts in the terminal, one for the server and one for the client.
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.48\textwidth]{images/RobotSimulation.png}}
+\caption{NAO robot in the Choreographe simulator.}
+\label{RobotSimulation}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=0.4\textwidth]{images/RobotWorking.png}}
+    \caption{NAO robot moving.}
+    \label{RobotWorking}
+    \end{figure}
+
+We used a webcam and videos to see the angles that are being sent to the robot. To first initaite the application you have to run the server part, using a python 2.7 interpreter. 
+This can be done using the following command, in which you have to specify the ip address of the robot as an argument:
+\begin{verbatim}
+    python2 server.py "ip_address"
+\end{verbatim}
+Then you have to run the client part, using a python 3.10 interpreter. 
+If you want to send the landmarks using a webcam you can use the following command:
+\begin{verbatim}
+    python3 client.py 
+\end{verbatim}
+On the other hand, if you want to send the landmarks using a video you can use the following command:
+\begin{verbatim}
+    python3 client.py "path_to_video"
+\end{verbatim}
+
+Sometimes the robot falls and if this occurs the application might not work or would stop working, so we had to be careful about this, because sudden movements of the robot could make it fall. 
+If the application stops working, there is no other option than to restart the application repeating the steps above.
 
@@
 \section{Conclusion and future work}
+Even though the project is not finished, we think is a good start for just using computer vision to apply it in robotics.
+\\
+There is a lot of work to do, such as improving the calculation of the angles or use both inverse kinematics and programming the angles to move the robot.
+\\
+In order to use the legs of the robot is necessary to do further research, because we have to consider many other things such as the mass center of the robot, and take care that the movements are not too abrupt to make the robot fall.
 
@@
 \section*{Acknowledgment}
-
-The authors would like to thank the support of the Hof University of Applied Science and the support of the Applied Robotics department.
+We want to thank my proffesor, Dr.
+Christian Groth for helping us during the project and thank also to the Hof University of Applied Science for giving us the opportunity to work with the NAO robot, which was a great experience.
 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+
+\bibitem{b1} NAOqi API, \textit{http://doc.aldebaran.com/2-5/naoqi/motion/index.html}
+\bibitem{b2} Mediapipe Pose Landmarking\textit{https://developers.google.com/mediapipe
+/solutions/vision/pose\_landmarker}
+\bibitem{b3}I.
+Irigoyen, "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad," Trabajo Fin de Grado, Facultad de Informática, Grado de Ingeniería Informática, Universidad del País Vasco, 2020.
+
 \end{thebibliography}

### 2024-02-14 Paper/main.tex
[update] paper

@@
 % Begin with the computer vision part and the NAOqi API part
-In the beginning, the computer vision part was done very easily, because Mediapipe has a lot of usage examples and good documentation.
-On the other hand working with the NAO robot was a much more difficult.
+In the beginning, the computer vision part was done very easily, because Mediapipe has a lot of usage examples and good documentation, such as the video "AI Pose Estimation with Python and MediaPipe"\cite{b4}, that helped us a lot on getting the landmarks and calculate some angles.
+On the other hand working with the NAO robot was a much more difficult, because we did not know how to start.
 \\
@@
 Irigoyen, "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad," Trabajo Fin de Grado, Facultad de Informática, Grado de Ingeniería Informática, Universidad del País Vasco, 2020.
+\bibitem{b4} Nicholas Renotte - Robotics and AI, "AI Pose Estimation with Python and MediaPipe," YouTube, 2021. [Online]. Available: https://www.youtube.com/watch?v=06TE\_U21FK4&t=2109s&ab\_channel=
+NicholasRenotte.
 

### 2024-02-14 Paper/main.tex
[update] files order

@@
 \begin{abstract}
-In this project we made a NAO robot, from Aldebaran, move imitating human movements. This movements were captured with a webcam using Mediapipe.
-Though this human imitation has already been done, we wanted to make it in a different way. Because most of the other projects use multiple cameras or depth sensors, such as the LIDAR sensor. 
-The project is way far from being finished, because the robot only moves his arms and not very precisely. But we think is a good start for future work on computer vision and robotics.
+In this project, we programmed a NAO robot from Aldebaran to mimic human movements captured by a webcam using Mediapipe.
+While this type of human imitation has been done before, we aimed to approach it differently.
+Unlike most other projects utilizing multiple cameras or depth sensors like the LIDAR sensor, our focus was on a novel methodology.
+The project is still in progress, with the robot currently capable of moving its arms, albeit not with high precision.
+Nonetheless, we see this as a promising starting point for future developments in computer vision and robotics.
 \end{abstract}
@@
 \section{State of the art}
-In this section we will describe different ways to move a NAO robot the Mediapipe Framework and a work related to human imitation using the NAO robot.
+In this section, we will explore various methods for controlling the movement of a NAO robot using the Mediapipe Framework, as well as discuss related work involving human imitation with the NAO robot.
 
-The NAO robot docomentation  \cite{b1} states that there is two ways to move the NAO robot to do poses.
-The first one is using the angles from the joints and the second one is using inverse kinematics.
-Though there is more ways to move the robot, those are more for walking or to perform a predefined pose.
+According to the NAO robot documentation \cite{b1}, there are two primary methods for posing the NAO robot: using joint angles and employing inverse kinematics.
+While other methods exist for walking or performing predefined poses, these two are fundamental to our project's scope.
 
-There is  two ways to control the effectors to perform a pose, regardless we use inverse kinematics or not, which are:
+Regardless of whether inverse kinematics is employed, there are two main ways to control the effectors to achieve a pose:
 \begin{itemize}
-    \item Animation methods, in which the time is fixed and there are blocking functions.
-    \item Reactive methods, that can be used to control the robot in real time, and there are non-blocking functions.
+    \item Animation methods, which operate within fixed time frames and involve blocking functions.
+    \item Reactive methods, suitable for real-time control with non-blocking functions.
 \end{itemize}
 
-We have various functions contained in the \textit{ALMotionProxy} module, related to the movement by controlling the joints some of the animation methods are:
+Within the \textit{ALMotionProxy} module, numerous functions pertain to joint movement. Some notable animation methods include:
 \begin{itemize}
-    \item \textit{ALMotionProxy.angleInterpolation}, that allows you to move the robot from a specific position to another in a specific time.
-    \item \textit{ALMotionProxy.angleInterpolationWithSpeed}, that allows you to move the robot from a specific position to another in a specific time and speed.
+    \item \textit{ALMotionProxy.angleInterpolation}, enabling movement from one specific position to another within a specified time.
+    \item \textit{ALMotionProxy.angleInterpolationWithSpeed}, facilitating movement between specific positions within defined time and speed parameters.
 \end{itemize}
-One important method is:
+An essential method is:
 \begin{itemize}
-    \item \textit{ALMotionProxy.setAngles}, that allows you to move set the angles of a single joint or a set of joints of the robot.
+\item \textit{ALMotionProxy.setAngles}, enabling the manipulation of single joint angles or sets of joint angles on the robot.
 \end{itemize}
 
-As it was stated before the robot can be controlled using inverse kinematics as well, in this case a classical IK solver which uses only the joints of the effector chain to reach a target and a generalized IK solver (also called Whole Body control) which uses all the robot joints to reach a target.
-Some of the animation and reactive methods related to the inverse kinematics that we consider important are:
+Furthermore, the robot's control extends to inverse kinematics.
+Here, classical IK solvers and generalized IK solvers (Whole Body control) are employed.
+Some pertinent animation and reactive methods related to inverse kinematics include:
 \begin{itemize}
-    \item \textit{ALMotionProxy.positionInterpolation} that allows you to move the robot from a specific position to another in a specific time 
-    \item \textit{ALMotionProxy.setPosition}, that allows you to move the robot to a specific position in a 3d space.
+    \item \textit{ALMotionProxy.positionInterpolation}, facilitating movement between specific positions within a specified time frame.
+    \item \textit{ALMotionProxy.setPosition}, enabling precise positioning of the robot in 3D space.
 \end{itemize}
 
-BlazePose \cite{b2}, is and architecture for single person 3D pose detection based in convolutional neural networks.
-It is available in the Mediapipe framework.
-And allows you to detect poses from a video or an image.
-There are 33 landmarks that the BlazePose model can detect (See figure \ref{fig:landmarksMP}). 
+BlazePose \cite{b2} is an architecture for single-person 3D pose detection based on convolutional neural networks.
+It is integrated into the Mediapipe framework, enabling the detection of poses from videos or images.
+The model is capable of detecting 33 landmarks (see Figure \ref{fig:landmarksMP}), which can be interpreted as points in a 3D space.
+
 \begin{figure}[htbp]
@@
 \end{figure}
-These landmarks can be read as a set of points in a 3D space.
-The Landmarker has various configuration options, such as:
+
+The Landmarker offers various configuration options, including:
+
 \begin{itemize}
-\item \textit{model\_complexity},  that allows you to choose between three different models, the lite, the full and the heavy. Depending on the model chosen the accuracy and the speed can increase.
-\item \textit{min\_detection\_confidence}, that allows you to set the minimum confidence that a pose is detected.
-\item \textit{min\_tracking\_confidence}, that allows you to set the minimum confidence that a pose is tracked.
+\item \textit{model\_complexity}, This parameter allows selection among three different models - lite, full, and heavy. Depending on the chosen model, both accuracy and speed can vary.
+\item \textit{min\_detection\_confidence}, It enables setting the minimum confidence level required for detecting a pose.
+\item \textit{min\_tracking\_confidence}, This parameter allows setting the minimum confidence level required for tracking a pose.
 \end{itemize}
 
-In a thesis called "
-Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad"\cite{b3} the authors use the NAO robot to imitate the movements of a human using a kinect sensor. 
-They use a client-server approach to send the data from the kinect sensor to the robot through the NAOqi API.
-In the client part they use the \textit{pykinect2} library to get the data from the kinect sensor, this data are 25 landmarks that represent the human body.
-These data is then sent to the server part using the \textit{socket} library.
-In the server part they calculate the angles between the joints and then send them to the robot using the \textit{ALMotionProxy.AngleInterpolation} method.
-
+In a thesis titled "Mimetización de movimiento por robot antropomorfo basado en imágenes de sensor de profundidad" \cite{b3}, the authors utilize the NAO robot to mimic human movements using a Kinect sensor.
+They adopt a client-server approach to transmit data from the Kinect sensor to the robot via the NAOqi API.
+In the client-side implementation, they employ the \textit{pykinect2} library to retrieve data from the Kinect sensor, which consists of 25 landmarks representing the human body.
+This data is then relayed to the server-side using the \textit{socket} library.
+On the server-side, the angles between the joints are computed and transmitted to the robot using the \textit{ALMotionProxy.AngleInterpolation} method.
 % intrduccion: poner en contexto al lector sobre el tema

### 2024-02-14 misc/GetAnglesNew.py

@@ -1,0 +1,200 @@
+#program to see the angles of the robot on the screen and send them to the robot
+# it can detect camera as well as a video
+import cv2
+import mediapipe as mp
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+import time
+import random
+def plotsomethinginrandom3d(fig):
+    x=np.random.rand(10)
+    y=np.random.rand(10)
+    z=np.random.rand(10)
+    ax.set_xlabel('X Label')
+    ax.set_ylabel('Y Label')
+    ax.set_zlabel('Z Label')
+    ax = fig.add_subplot(111, projection='3d')
+    ax.scatter(x, y, z, c='r', marker='o')
+    plt.show()
+    print(x,y,z)    
+
+def angle_between_vectors(v1, v2, normal_vector):
+    v1 = np.array(v1)
+    v2 = np.array(v2)
+    normal_vector = np.array(normal_vector)
+
+    # Resto del código sigue igual...
+    proj_v1 = v1 - np.dot(v1, normal_vector) / np.linalg.norm(normal_vector)**2 * normal_vector
+    proj_v2 = v2 - np.dot(v2, normal_vector) / np.linalg.norm(normal_vector)**2 * normal_vector
+    cos_theta = np.dot(proj_v1, proj_v2) / (np.linalg.norm(proj_v1) * np.linalg.norm(proj_v2))
+    angle_rad = np.arccos(np.clip(cos_theta, -1.0, 1.0))
+    angle_deg = np.degrees(angle_rad)
+
+    return angle_deg
+
+
+def angleRShoulderPitch(Lshoulder,Rhip,Rshoulder,Relbow): #calulates the Shoulderpitch value for the Left shoulder by using geometry
+    # get the vector from the shoulder to the elbow
+    upper_arm = [Relbow[0] - Rshoulder[0], Relbow[1] - Rshoulder[1], Relbow[2] - Rshoulder[2]]
+    # get the vector from the shoulder to the hip
+    shoulder_hip = [Rhip[0] - Rshoulder[0], Rhip[1] - Rshoulder[1], Rhip[2] - Rshoulder[2]]
+    #get the vector from the left shoulder to the right shoulder
+    shoulder_shoulder = [Lshoulder[0] - Rshoulder[0], Lshoulder[1] - Rshoulder[1], Lshoulder[2] - Rshoulder[2]]
+    # calculate the angle between the vectors
[…]

### 2024-02-14 misc/MoveRobot.py

@@ -1,0 +1,104 @@
+# import naoqi
+# from naoqi import ALProxy
+# import math
+# #program to see the angles in the robot
+# RobotIP = "salvadors-macbook-pro.local."
+# RobotPort = 9559
+# #Sends processed frames to the robot
+# def sendrobot(robotIP="192.168.171.141", PORT=9559):
+#     try:
+#         try:
+#             motionProxy = ALProxy("ALMotion", robotIP, PORT) #creates proxy to call specific functions
+#         except Exception, e:
+#             print "Could not create proxy to AlMotion"
+#             print "Error was: ", e
+#         try:
+#             postureProxy = ALProxy("ALRobotPosture", robotIP, PORT) #creates proxy to call specific functions
+#         except Exception, e:
+#             print "Could not create proxy to ALRobotPosture"
+#             print "Error was: ", e
+
+#         # set RShoulderpitch to 0.5 radians (28.6478897565 degrees)
+#         angle = -119
+#         angle=math.radians(angle)
+#         motionProxy.setAngles("RShoulderPitch", angle, 0.5)
+#         postureProxy.goToPosture("StandInit", 0.5)
+#         angle = -76
+#         angle=math.radians(angle)
+#         motionProxy.setAngles("RShoulderRoll", angle, 0.5)
+#     except Exception, e:
+#         print "Could not create proxy to ALMotion"
+#         print "Error was: ", e
+
+        
+# if __name__ == "__main__":
+#     sendrobot(RobotIP, RobotPort)
+
+#! /usr/bin/env python
+# -*- encoding: UTF-8 -*-
+
+"""Example: Use transformInterpolations Method on Arm"""
+
+import qi
+import argparse
+import sys
+import motion
+# import almath
+import math
+
+
+
+def main(session):
+    """
+    Use case of transformInterpolations API.
+    """
+    # Get the services ALMotion & ALRobotPosture.
+
+    motion_service = session.service("ALMotion")
+    posture_service = session.service("ALRobotPosture")
+
+    # Wake up robot
+    motion_service.wakeUp()
+
+    # Send robot to Stand Init
+    posture_service.goToPosture("StandInit", 0.5)
+
+    effector   = "LArm"
+    frame      = motion.FRAME_TORS
+    axisMask   = almath.AXIS_MASK_VEL # just control position
+    useSensorValues = False
+
+    path = []
+    currentTf = motion_service.getTransform(effector, frame, useSensorValues)
[…]

### 2024-02-14 misc/getAngles.py

@@ -1,0 +1,285 @@
+
+import cv2
+import mediapipe as mp
+import numpy as np
+import math
+import socket
+import time
+import pickle
+from threading import Thread
+
+#Program to try and vis
+
+
+def angleRShoulderPitch(Rshoulder,Relbow): #calulates the Shoulderpitch value for the Left shoulder by using geometry
+    x2 = Rshoulder[0]
+    y2 = Rshoulder[1]
+    z2 = Rshoulder[2]
+    x1 = Relbow[0]
+    y1 = Relbow[1]
+    z1 = Relbow[2]
+    if(y2>y1):
+        angle = math.atan(abs(y2 - y1) / abs(z2 - z1)) 
+        angle = math.degrees(angle)
+        angle = -(angle)
+        if(angle<-118):
+            angle = -117
+        return angle
+    else:
+        angle = math.atan((z2-z1)/(y1-y2))
+        angle = math.degrees(angle)
+        angle = 90-angle
+        return angle
+
+
+def angleRShoulderRoll(Rshoulder,Relbow): #calulates the ShoulderRoll value for the Right shoulder by using geometry
+    x2 = Rshoulder[0]
+    y2 = Rshoulder[1]
+    z2 = Rshoulder[2]
+    x1 = Relbow[0]
+    y1 = Relbow[1]
+    z1 = Relbow[2]
+    if(z2<z1):
+        test = z2
+        anderetest = z1
+        z2=anderetest
+        z1=test
+    if (z2 - z1 < 0.1):
+        z2 = 1.0
+        z1 = 0.8
+    angle = math.atan((x1 - x2) / (z2 - z1))
+    angle = math.degrees(angle)
+    return angle
+
+def angleRElbowRoll(Rshoulder,Relbow,Rwrist): #calulates the ElbowRoll value for the Right elbow by using geometry
+    x3 = Rshoulder[0]
+    y3 = Rshoulder[1]
+    z3 = Rshoulder[2]
+    x2 = Relbow[0]
+    y2 = Relbow[1]
+    z2 = Relbow[2]
+    x1 = Rwrist[0]
+    y1 = Rwrist[1]
+    z1 = Rwrist[2]
+
+
+    a1=(x3-x2)**2+(y3-y2)**2 + (z3-z2)**2 
+    lineA= a1 ** 0.5                        # calculates length of line between 2 3D coordinates
+    b1=(x2-x1)**2+(y2-y1)**2 + (z2-z1)**2
[…]

### 2024-02-14 GetAnglesNew.py
[delete] all the other files

@@ -1,200 +1,0 @@
-#program to see the angles of the robot on the screen and send them to the robot
-# it can detect camera as well as a video
-import cv2
-import mediapipe as mp
-import numpy as np
-import matplotlib.pyplot as plt
-import sys
-import time
-import random
-def plotsomethinginrandom3d(fig):
-    x=np.random.rand(10)
-    y=np.random.rand(10)
-    z=np.random.rand(10)
-    ax.set_xlabel('X Label')
-    ax.set_ylabel('Y Label')
-    ax.set_zlabel('Z Label')
-    ax = fig.add_subplot(111, projection='3d')
-    ax.scatter(x, y, z, c='r', marker='o')
-    plt.show()
-    print(x,y,z)    
-
-def angle_between_vectors(v1, v2, normal_vector):
-    v1 = np.array(v1)
-    v2 = np.array(v2)
-    normal_vector = np.array(normal_vector)
-
-    # Resto del código sigue igual...
-    proj_v1 = v1 - np.dot(v1, normal_vector) / np.linalg.norm(normal_vector)**2 * normal_vector
-    proj_v2 = v2 - np.dot(v2, normal_vector) / np.linalg.norm(normal_vector)**2 * normal_vector
-    cos_theta = np.dot(proj_v1, proj_v2) / (np.linalg.norm(proj_v1) * np.linalg.norm(proj_v2))
-    angle_rad = np.arccos(np.clip(cos_theta, -1.0, 1.0))
-    angle_deg = np.degrees(angle_rad)
-
-    return angle_deg
-
-
-def angleRShoulderPitch(Lshoulder,Rhip,Rshoulder,Relbow): #calulates the Shoulderpitch value for the Left shoulder by using geometry
-    # get the vector from the shoulder to the elbow
-    upper_arm = [Relbow[0] - Rshoulder[0], Relbow[1] - Rshoulder[1], Relbow[2] - Rshoulder[2]]
-    # get the vector from the shoulder to the hip
-    shoulder_hip = [Rhip[0] - Rshoulder[0], Rhip[1] - Rshoulder[1], Rhip[2] - Rshoulder[2]]
-    #get the vector from the left shoulder to the right shoulder
-    shoulder_shoulder = [Lshoulder[0] - Rshoulder[0], Lshoulder[1] - Rshoulder[1], Lshoulder[2] - Rshoulder[2]]
-    # calculate the angle between the vectors
[…]

### 2024-02-14 MoveRobot.py

@@ -1,104 +1,0 @@
-# import naoqi
-# from naoqi import ALProxy
-# import math
-# #program to see the angles in the robot
-# RobotIP = "salvadors-macbook-pro.local."
-# RobotPort = 9559
-# #Sends processed frames to the robot
-# def sendrobot(robotIP="192.168.171.141", PORT=9559):
-#     try:
-#         try:
-#             motionProxy = ALProxy("ALMotion", robotIP, PORT) #creates proxy to call specific functions
-#         except Exception, e:
-#             print "Could not create proxy to AlMotion"
-#             print "Error was: ", e
-#         try:
-#             postureProxy = ALProxy("ALRobotPosture", robotIP, PORT) #creates proxy to call specific functions
-#         except Exception, e:
-#             print "Could not create proxy to ALRobotPosture"
-#             print "Error was: ", e
-
-#         # set RShoulderpitch to 0.5 radians (28.6478897565 degrees)
-#         angle = -119
-#         angle=math.radians(angle)
-#         motionProxy.setAngles("RShoulderPitch", angle, 0.5)
-#         postureProxy.goToPosture("StandInit", 0.5)
-#         angle = -76
-#         angle=math.radians(angle)
-#         motionProxy.setAngles("RShoulderRoll", angle, 0.5)
-#     except Exception, e:
-#         print "Could not create proxy to ALMotion"
-#         print "Error was: ", e
-
-        
-# if __name__ == "__main__":
-#     sendrobot(RobotIP, RobotPort)
-
-#! /usr/bin/env python
-# -*- encoding: UTF-8 -*-
-
-"""Example: Use transformInterpolations Method on Arm"""
-
-import qi
-import argparse
-import sys
-import motion
-# import almath
-import math
-
-
-
-def main(session):
-    """
-    Use case of transformInterpolations API.
-    """
-    # Get the services ALMotion & ALRobotPosture.
-
-    motion_service = session.service("ALMotion")
-    posture_service = session.service("ALRobotPosture")
-
-    # Wake up robot
-    motion_service.wakeUp()
-
-    # Send robot to Stand Init
-    posture_service.goToPosture("StandInit", 0.5)
-
-    effector   = "LArm"
-    frame      = motion.FRAME_TORS
-    axisMask   = almath.AXIS_MASK_VEL # just control position
-    useSensorValues = False
-
-    path = []
-    currentTf = motion_service.getTransform(effector, frame, useSensorValues)
[…]

### 2024-02-14 getAngles.py

@@ -1,285 +1,0 @@
-
-import cv2
-import mediapipe as mp
-import numpy as np
-import math
-import socket
-import time
-import pickle
-from threading import Thread
-
-#Program to try and vis
-
-
-def angleRShoulderPitch(Rshoulder,Relbow): #calulates the Shoulderpitch value for the Left shoulder by using geometry
-    x2 = Rshoulder[0]
-    y2 = Rshoulder[1]
-    z2 = Rshoulder[2]
-    x1 = Relbow[0]
-    y1 = Relbow[1]
-    z1 = Relbow[2]
-    if(y2>y1):
-        angle = math.atan(abs(y2 - y1) / abs(z2 - z1)) 
-        angle = math.degrees(angle)
-        angle = -(angle)
-        if(angle<-118):
-            angle = -117
-        return angle
-    else:
-        angle = math.atan((z2-z1)/(y1-y2))
-        angle = math.degrees(angle)
-        angle = 90-angle
-        return angle
-
-
-def angleRShoulderRoll(Rshoulder,Relbow): #calulates the ShoulderRoll value for the Right shoulder by using geometry
-    x2 = Rshoulder[0]
-    y2 = Rshoulder[1]
-    z2 = Rshoulder[2]
-    x1 = Relbow[0]
-    y1 = Relbow[1]
-    z1 = Relbow[2]
-    if(z2<z1):
-        test = z2
-        anderetest = z1
-        z2=anderetest
-        z1=test
-    if (z2 - z1 < 0.1):
-        z2 = 1.0
-        z1 = 0.8
-    angle = math.atan((x1 - x2) / (z2 - z1))
-    angle = math.degrees(angle)
-    return angle
-
-def angleRElbowRoll(Rshoulder,Relbow,Rwrist): #calulates the ElbowRoll value for the Right elbow by using geometry
-    x3 = Rshoulder[0]
-    y3 = Rshoulder[1]
-    z3 = Rshoulder[2]
-    x2 = Relbow[0]
-    y2 = Relbow[1]
-    z2 = Relbow[2]
-    x1 = Rwrist[0]
-    y1 = Rwrist[1]
-    z1 = Rwrist[2]
-
-
-    a1=(x3-x2)**2+(y3-y2)**2 + (z3-z2)**2 
-    lineA= a1 ** 0.5                        # calculates length of line between 2 3D coordinates
-    b1=(x2-x1)**2+(y2-y1)**2 + (z2-z1)**2
[…]

### 2024-02-14 Paper/main.tex
[write] new main.pdf not editable

@@
 \end{abstract}
-
 \begin{IEEEkeywords}
@@
 \begin{figure}[htbp]
+    \label{fig:landmarksMP}
     \centerline{\includegraphics[width=0.48\textwidth]{images/landmarksMP.jpeg}}
     \caption{Landmarks from the Mediapipe library.}
-\label{fig:landmarksMP}
 \end{figure}
@@
 \section{Approach}
-
 \subsection{Objectives}
@@
 \begin{figure}[htbp]
+    \label{fig:RightArmAngles}
     \centerline{\includegraphics[width=0.5\textwidth]{images/RightArmAngles.jpeg}}
-    \caption{Landmarks from the Mediapipe library.}
-    \label{fig:RightArmAngles}
+    \caption{Joints in the arm of the NAO robot.}
 \end{figure}
@@
 We decided to use sockets to send the data, as we got inspiration from a project that we found with a similiar approach, in which the author used sockets to send the data from a kinect sensor to the robot.
-This solved everything, about the connection between the scripts, because it uses the client-server approach, allowing me to use python 3.10 for the computer vision part that is the client and python 2.7 for the Robot movement part that is the server.
+This solved everything, about the connection between the scripts, because it uses the client-server approach, allowing us to use python 3.10 for the computer vision part that is the client and python 2.7 for the Robot movement part that is the server.
 We just had to do some encoding to send the data.
@@
 As we said before after changing a lot the parameters and definition of the functions that were implemented before we realized that we was not sending the right data to the robot from the server, so we decided to change the approach and instead of sending the coordenates of the landmarks to the server, we decided to send the angles between them and send them directly to the server.
-This would help me to see what angles we was sending to the robot by showing them on the displayed image.
+This would help us to see what angles we was sending to the robot by showing them on the displayed image.
 
@@
 % diferencias entre mi proyecto y los otros y como contribuye mi proyecto al estado del arte
-The main difference between my project and the others is that it has a different approach to solve the problem, relying only on one camera and machine learning to detect and recreate the human poses, instead of using a lot of sensors.
+The main difference between our project and the others is that it has a different approach to solve the problem, relying only on one camera and machine learning to detect and recreate the human poses, instead of using a lot of sensors.
 This is a contribution to the state of the art, because it implies that if there were better machine learning models, the robot could imitate the human movements in a better way.
@@
 \section*{Acknowledgment}
-We want to thank my proffesor, Dr.
+We want to thank our proffesor, Dr.
 Christian Groth for helping us during the project and thank also to the Hof University of Applied Science for giving us the opportunity to work with the NAO robot, which was a great experience.
